The Art of Robotics:\\\vspace{0.2em}\huge{Toward a Holistic Approach}

### 2018-08-02 ms-thesis-slides.tex
talk done!

%!TEX program = lualatex
\documentclass[aspectratio=169]{beamer}
% add 'handout' to beamer options for printout

@@

			\item Touching Robots
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}

			\item Conclusions
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}

@@

		\begin{frame}
			\frametitle{Problem 1: What is a Robot?}
			\begin{itemize}
				\item I know it's a cliché to bring this up\dots \pause but I must! \pause
				\begin{itemize}
					\item Does the ambiguity really matter? \pause
					\item Maybe not, but some unifying \emph{theme} would be useful!
				\end{itemize}
			\end{itemize}
		\end{frame}

@@

		\begin{frame}
			\frametitle{Problem 3: Locomotion and Manipulation, United}
			\begin{itemize}
				\item Not a terribly practical insight\dots \pause~but thinking back to \emph{Problem 1}\dots
			\end{itemize}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center,text width=0.8\textwidth,align=center] (loco-manip) at ($(current page.center)+(0,-10mm)$) {So locomotion is just a subset of manipulation!};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{Embodiment \& Hogan's Physical-Equivalence Principle}
			\begin{itemize}[<+->]
				\item Embodiment
					\begin{itemize}
						\item 
						\item Presently resides in the cognitive science community (as in ``embodied \emph{cognition}'')
					\end{itemize}
				\item 
			\end{itemize}
		\end{frame}

	\section{A Unifying Framework}
		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}
				\item Port-based Analysis
					\begin{itemize}
						\item Inherits the bond-graph notion of power ports
						\item Treats systems in terms of power flow between components
						\item Each bond represents the conjugate pair of an effort and flow
					\end{itemize}\pause
				\item Hamiltonian Dynamics
					\begin{itemize}
						\item Provides a fully geometric (intrinsic, coordinate free) description of system dynamics
						\item Equivalent to (and convertible from/to) Lagrangian formulation
							\begin{itemize}
								\item Whereas Lagrangian dynamics derives solely from variation principles, the Hamiltonian formulation 
								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved.
								\item Configuration space of Lagrangian dynamics replaced with state space
							\end{itemize}
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Bond-Graphs}

		\end{frame}

		\begin{frame}
			\frametitle{Hamiltonian Dynamics}

		\end{frame}

		\begin{frame}
			\frametitle{Dissipative Elements}
		\end{frame}

		\begin{frame}
			\frametitle{Putting it All Together}

		\end{frame}

	\section{Touching Robots}

		\begin{frame}
			\frametitle{A Note on Stiffness and Collisions}
			\begin{itemize}
				\item \textbf{\color{red}STOP COLLIDING STIFF OBJECTS AND EXPECTING RELIABLE RESULTS}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{The Most Important Sensory Modality}
		\end{frame}

		\begin{frame}
			\frametitle{Contact Models}
		\end{frame}

		\begin{frame}
			\frametitle{Terminator 2 Got It Right}
			\begin{center}
			\movie[height = 0.6\textwidth, width = 0.8\textwidth,showcontrols]{}{media/terminator2-pain.mp4}
			\end{center}
		\end{frame}

	\section{Closing Thoughts}
		\begin{frame}
			\frametitle{Closing Thoughts}
			\begin{itemize}
				\item Woo, Beamer!
			\end{itemize}
		\end{frame}

@@

	\begin{frame}
	\frametitle{Cheers}
		Committee\\Lab\\The other profs\\Jean\\Cameron\\Cats\\Parents for debt free education
	\end{frame}

@@

	\section{Other Things}
	\begin{frame}
	\frametitle{Teaching with CMU's Gelfand Outreach Center}
	\begin{tikzpicture}[overlay, remember picture]
	\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
	\end{tikzpicture}
	\vspace{9em}
	\begin{itemize}
		\item Introduction to Robotics with the Finch Platform
		\begin{itemize}
			\item Each session is 5 days, 3 hrs/day
			\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
			\item 1 session Summer 2017 + 2 sessions Summer 2018
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Teaching with CMU's Gelfand Outreach Center}
\begin{tikzpicture}[overlay, remember picture]
\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
\end{tikzpicture}
\vspace{9em}
\begin{itemize}
\item Saturday Series LEGO WeDo Robotics
\begin{itemize}
	\item 3 hour course
	\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
	\item 1 session Spring 2018
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Robotics Institute Meme Facebook Page}
\begin{tikzpicture}[overlay, remember picture]
\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
\end{tikzpicture}
\end{frame}

\begin{frame}
\frametitle{Robotics Institute Meme Facebook Page}
\vspace{9em}
\begin{itemize}
\item Some statistics:
\begin{itemize}
\item The RI's first and only meme page
\item Formed in March 2018
\item 170 members
\item 30 memes, 23 original contributions!
\end{itemize}
\end{itemize}
\begin{tikzpicture}[overlay, remember picture]
\node[anchor=south east] (ri-meme-3) at ($(current page.south east) + (2mm,5mm)$) {\includegraphics[width=7.5cm]{media/ri-meme-manifold-optimization.jpg}};
\end{tikzpicture}
\begin{tikzpicture}[overlay, remember picture]
\node[anchor=north east] (ri-meme-1) at ($(current page.north east) + (-45mm,-12mm)$) {\includegraphics[width=3.5cm]{media/ri-meme-thesis-anxiety.jpg}};
\end{tikzpicture}
\begin{tikzpicture}[overlay, remember picture]
\node[anchor=north west] (ri-meme-2) at ($(current page.north west) + (10mm,-12mm)$) {\includegraphics[width=5cm]{media/ri-meme-ros-sleep.jpg}};
\end{tikzpicture}
\end{frame}

>>>>

%!TEX program = lualatex
\documentclass[aspectratio=169,handout]{beamer}
% add 'handout' to beamer options for printout

@@

%			\item Touching Robots
%				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}
%			
			\item Conclusions
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}

@@

		\begin{frame}
			\frametitle{Problem 1: What is a Robot?}
			\begin{itemize}
				\item I know it's a cliché to bring this up\dots \pause~but I must! \pause
				\begin{itemize}
					\item Does the ambiguity really matter? \pause
					\item Maybe not, but some unifying \emph{theme} would be useful!
				\end{itemize}
			\end{itemize}
		\end{frame}

@@

		\begin{frame}
			\frametitle{Problem 3: Locomotion and Manipulation, United}
			\begin{itemize}
				\item Not a terribly practical insight\dots \pause~but thinking back to \emph{Problem 1}\dots
			\end{itemize}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center,text width=0.8\textwidth,align=center] (manip-is-king) at ($(current page.center)+(0,-10mm)$) {\Large \color{red} Manipulation \emph{is} the central theme in robotics!};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{Embodiment \& Hogan's Physical-Equivalence ``Postulate''}
			\begin{itemize}[<+->]
				\item Embodiment
					\begin{itemize}
						\item Vaguely, the idea that robots exist in the real world and are inherently tied to their environment
						\item Presently resides in the cognitive science community (as in ``embodied \emph{cognition}'')
					\end{itemize}
				\item \emph{Hogan's} Physical-Equivalent Principle
					\begin{itemize}
						\item ``It is impossible tO devise a controller which will cause a physical system to present an apparent behavior 10 its environment which is distinguishable from that of a purely physical system'' \autocite{hogan1985impedance}
						\item Basic argument for this is ``you can't break thermodynamic laws''
						\item But more intuitively, the robot is a real thing, you can't make it do not real things
					\end{itemize}
			\end{itemize}
		\end{frame}

	\section{A Unifying Framework}
		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}[<+->]
				\item The symbiosis of:
					\begin{itemize}[<+->]
						\item Bond graph theory (\emph{Paynter, Hogan, Breedveld, van Dijk})
						\item Hamiltonian dynamics on manifolds (i.e. ``geometric mechanics'')
						\item Poisson / Dirac structures
					\end{itemize}
				\item Principal contributors include \emph{Stramigioli, van der Schaft, Maschke}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}
				\item Port-based Analysis
					\begin{itemize}
						\item Inherits the bond-graph notion of power ports
						\item Treats systems in terms of power flow between components
						\item Each bond represents the conjugate pair of an effort and flow
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}
				\item Hamiltonian Dynamics
					\begin{itemize}
						\item Provides a fully geometric (intrinsic, coordinate free) description of system dynamics
						\item Equivalent to (and convertible from/to) Lagrangian formulation, but better!
							\begin{itemize} 
								\item Riemannian geometry of Lagrangian dynamics replaced with symplectic geometry, in which fundamental invariants are preserved
								\item Configuration space of Lagrangian dynamics replaced with state space
								\item Hamiltonian formulation directly yields a system of first order differential equations
							\end{itemize}
						\item Avoiding nonholonomic constraints yields explicit ODE\footnote{May be a stiff explicit ODE! So, soften your intermittent contacts!}
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Port-Hamiltonian Systems Theory}
			\begin{itemize}
				\item System fully defined by: 
					\begin{itemize}
						\item Energy function captures all energy storage elements in system
						\item Resistive structure captures all dissipative elements in system
						\item Poisson or Dirac interconnection structure defines power flow within system
							\begin{itemize}
								\item \emph{Storage port} connects to energy storage
								\item \emph{Dissipative port} connects to resistive structure
								\item \emph{Interaction port} connects to environment (\textbf{dynamic system} not known a-priori or directly controlled)
								\item \emph{Controller port} connects to controller (\textbf{dynamic system} that the designer has control over)
							\end{itemize}
					\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Working Through an Example}
		\end{frame}

	\section{Closing Thoughts}
		\begin{frame}
			\frametitle{Closing Thoughts}
			\begin{itemize}
				\item Manipulation is the common theme in robotics
				\item Embodiment \Leftrightarrow Hogan's Physical Equivalence Principle \autocite{hogan1985impedance}
				\item Port-Hamiltonian Systems Theory is the framework to unify robotics
			\end{itemize}
		\end{frame}

@@

%		\begin{frame}
%	\frametitle{Teaching with CMU's Gelfand Outreach Center}
%	\begin{tikzpicture}[overlay, remember picture]
%	\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
%	\end{tikzpicture}
%	\vspace{9em}
%	\begin{itemize}
%		\item Introduction to Robotics with the Finch Platform
%		\begin{itemize}
%			\item Each session is 5 days, 3 hrs/day
%			\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
%			\item 1 session Summer 2017 + 2 sessions Summer 2018
%		\end{itemize}
%	\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Teaching with CMU's Gelfand Outreach Center}
%\begin{tikzpicture}[overlay, remember picture]
%\node[anchor=south east] (gelfand-logo) at ($(current page.south east) + (-8mm, 8mm)$) {\includegraphics[width=4cm]{media/gelfand-logo.jpg}};
%\end{tikzpicture}
%\vspace{9em}
%\begin{itemize}
%\item Saturday Series LEGO WeDo Robotics
%\begin{itemize}
%	\item 3 hour course
%	\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
%	\item 1 session Spring 2018
%\end{itemize}
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Robotics Institute Meme Facebook Page}
%\begin{tikzpicture}[overlay, remember picture]
%\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
%\end{tikzpicture}
%\end{frame}
%
%\begin{frame}
%\frametitle{Robotics Institute Meme Facebook Page}
%\vspace{9em}
%\begin{itemize}
%\item Some statistics:
%\begin{itemize}
%\item The RI's first and only meme page
%\item Formed in March 2018
%\item 170 members
%\item 30 memes, 23 original contributions!
%\end{itemize}
%\end{itemize}
%\begin{tikzpicture}[overlay, remember picture]
%\node[anchor=south east] (ri-meme-3) at ($(current page.south east) + (2mm,5mm)$) {\includegraphics[width=7.5cm]{media/ri-meme-manifold-optimization.jpg}};
%\end{tikzpicture}
%\begin{tikzpicture}[overlay, remember picture]
%\node[anchor=north east] (ri-meme-1) at ($(current page.north east) + (-45mm,-12mm)$) {\includegraphics[width=3.5cm]{media/ri-meme-thesis-anxiety.jpg}};
%\end{tikzpicture}
%\begin{tikzpicture}[overlay, remember picture]
%\node[anchor=north west] (ri-meme-2) at ($(current page.north west) + (10mm,-12mm)$) {\includegraphics[width=5cm]{media/ri-meme-ros-sleep.jpg}};
%\end{tikzpicture}
%\end{frame}

	\begin{frame}
	\frametitle{Cheers}
		\begin{itemize}
			\item Matt Mason
			\item Aaron Johnson \& Will Martin
			\item The MLab
			\item Ross Knepper, Hod Lipson, Ephrahim Garcia, Boris Kogan, Mike Meller
			\item Jean Harpley
			\item Cameron
			\item Malcolm X, Nina Simone, and George Harrison
			\item Parents
		\end{itemize}
	\end{frame}

@@
